Modal Abstractions for Virtualizing Memory Addresses

### 2025-07-15 examples_C.tex
+

;;pte_t *walkpgdir(pte_t *pml4, const void *va) {
... ;; Stack setup

@@

;;pte_t *pml4_entry = &pml4[PML4EX(va)]; // Virtual address of L4 entry(*\label{line:start_pml4_calc}*)
mov    -0x8[rbp],rsi; mov    -0x10[rbp],rdi; ;; Load pml4 and va
;; Extract 9-bit (0x1ff=511) L4 index from va, multiply by 8 (byte index), add to pml4 for entry address
shr    0x27,rdi; and    0x1ff,rdi; shl    0x3,rdi; add    rdi,rsi(*\label{line:end_pml4_calc}*)
mov    rsi,-0x18[rbp] ;; Store virt. addr. to local var pml4_entry; logical pml4_entry is physical!

@@

;;pte_t *pdp = pte_get_next_table(pml4_entry);
mov    -0x18[rbp],rdi; ...; callq  c0 <pte_get_next_table>(*\label{line:first_getnext_call}*)
;;save the physical next table address in rax

@@

$\specline{\texttt{rax}  \mapsto_{\textsf{r}} \textsf{table\_root(l4e\_val'.pfn)} }_{\rtv}$ ;; pte_get_next_table may have allocated a new page, updating entry
;;pte_t *pdp_entry = &pdp[PDPEX(va)]; // Virtual address of L3 entry

@@

... ;; Similar assembly & proofs for levels 3 and 2
... ;;return &pt[PTEX(va)]; // return address of L1 entry, similar index computation

>>>>

pte_t *walkpgdir(pte_t *pml4, const void *va) {
  /*... ;; Stack setup*/

@@

  pte_t *pml4_entry = &pml4[PML4EX(va)]; // Virtual address of L4 entry(*\label{line:start_pml4_calc}*)
  /*Load pml4 and va:*/
  /*Extract 9-bit (0x1ff=511) L4 index from va, multiply by 8 (byte index), add to pml4 for entry address (*\label{line:end_pml4_calc}*) */
  /*Store virt. addr. to local var pml4_entry; logical pml4_entry is physical!*/

@@

  pte_t *pdp = pte_get_next_table(pml4_entry); /*(*\label{line:first_getnext_call}*) save the physical next table address in rax*/

@@

  $\specline{\texttt{rax}  \mapsto_{\textsf{r}} \textsf{table\_root(l4e\_val'.pfn)} }_{\rtv}$
  /*pte_get_next_table may have allocated a new page, updating entry*/
  pte_t *pdp_entry = &pdp[PDPEX(va)]; /* Virtual address of L3 entry*/

@@

  /*... ;; Similar assembly & proofs for levels 3 and 2*/
  return &pt[PTEX(va)]; /* return address of L1 entry, similar index computation*/
